Demystifying Double Robust, Flexible Adjustment Methods for Causal Inference

### 2023-02-17 draft/ms-adj-draft-old.Rmd
new simulations + linear

```{r load}
# data from mx0.5
pisa <- readRDS('/Users/nathan/Google Drive/1 UCLA/Dissertation/diss-prop/data/pisa.rds') %>%
  mutate(age = as.numeric(age))

@@

perform <- function(est_df, label){
  est_df %>%
    summarize(bias = mean(d - truth),
              percent_bias = bias/sd(d),
              rmse = sqrt(mean(d - truth)^2),
              mae = median(abs(d - truth))) %>%
    mutate(label = label) %>%
    select(label, everything()) %>%
    return()
}
```

@@

>>>>

```{r load}
# data from mx0.5
pisa <- readRDS('/Users/nathan/My Drive/1 UCLA/Dissertation/diss-prop/data/pisa.rds') %>%
  mutate(age = as.numeric(age))

@@

perform <- function(est_df, label){
  est_df %>%
    summarize(bias = mean(d - truth),
              percent_bias = bias/sd(d),
              rmse = sqrt(mean(d - truth)^2),
              mae = median(abs(d - truth))) %>%
    mutate(label = label) %>%
    select(label, everything()) %>%
    return()
}

# dat <- sim_list
# i <- '3,1'
# 
# sim_dat <- data.frame(y = dat[[i]]$y, 
#                           d = ifelse(dat[[i]]$z == 'trt', 1, 0), 
#                           dat[[i]]$x)
# lm_out <- lm(y ~ d + ., sim_dat)
# lm_list[[i]] <- data.frame(d = lm_out$coefficients[['d']],
#                            truth = mean(dat[[i]]$y.1) - mean(dat[[i]]$y.0))

sim_linear <- list()
  for(j in 1:100){ # up to 100
    print(j)
    sim_linear[[j]] <- aciccomp2016::dgp_2016(aciccomp2016::input_2016, 
                                      3, j, extraInfo = T)

# sim_list <- sim_linear
```

@@

```{r dorie-results-linear}
bind_rows(
  read_csv(here('files', 'lm_df3.csv')),
  read_csv(here('files', 'psm_df3.csv')),
  read_csv(here('files', 'aipw_df3.csv')),
  read_csv(here('files', 'tmle_df3.csv')),
  read_csv(here('files', 'dml_df3.csv'))
  ) %>%
  select(-comp_time) %>%
  kableExtra::kable(booktabs = T, 
                    linesep = '',
                    caption = 'Results of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 5 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is average computation time measured in seconds for each dataset.')
```
